Group meetings

### 2023-09-14 diapo/15-09-23_meeting/main.tex
Few changes
Finished pres demain

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0cm] at (current page.34){
      \includegraphics[height=1cm]{../figures/ist.eps}
      \hspace{1pt}
      \includegraphics[height=1cm]{figures/inesc-mn.png}
      \includegraphics[height=1cm]{../figures/inesc-id.eps}
    };
  \end{tikzpicture}
}

@@

\begin{frame}
  \frametitle{Introduction}
  Quick introduction to your topic.

  \begin{itemize}
      \color{text}
    \item Briefly summarized your project. Some of the attendants may need some refresh.
    \item Explain in which project stage you are, thus we all know how close you are to achieve your goals.
  \end{itemize}

  ex: I have to design a PCB to control a magnetic sensor. I have already done the PCB and now I am testing it.
\end{frame}

@@

  Last meeting, I promised to do…

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{3cm} c c c }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task & \color{white}Done? & \color{white}Why not? & \color{white}Help? \\
    1 & test2 & test23 & test3 & test4\\
    2 & test2 & test23 & test3 & test4\\
    3 & test2 & test23 & test3 & test4\\
    4 & test2 & test23 & test3 & test4\\
    5 & test2 & test23 & test3 & test4\\
  \end{tabular}

\begin{frame}{What's new}
  \begin{itemize}
    \item Results obtianed :
      \begin{itemize}
          \color{text}
        \item
      \end{itemize}
    \item Improvements :
      \begin{itemize}
          \color{text}
        \item
      \end{itemize}
    \item Relevant information :
      \begin{itemize}
          \color{text}
        \item test
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Problems/doubts}
  \begin{itemize}
    \item Things that must me sorted out in order to continue with your work.\\ Explain the problem.
    \item Things that you do not understand.
  \end{itemize}
\end{frame}

@@

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    \color{white}\textbf{\#} & \centering\color{white}Task \cr
    1 & test23 \\
    2 & test23 \\
    3 & test23 \\
    4 & test23 \\
    5 & test23 \\
  \end{tabular}
\end{frame}

\begin{frame}{Networking and sharing}
  \begin{tikzpicture}
    \leftRect{Help/Collaboration :}{- If anybody has any idea of an interesting LSTM/NN problem to work on.\\-Also if any phenomen happening are familiar to you, I'll take the help}
    \rightRect{Recommendations :}{I worked on a latex/beamer version of the template}
  \end{tikzpicture}
\end{frame}

>>>>

\logo{
  \begin{tikzpicture}[overlay,remember picture]
    \node[left=0cm] at (current page.34){
      \includegraphics[height=1cm]{logos/ist.eps}
      \hspace{1pt}
      \includegraphics[height=1cm]{logos/inesc-mn.png}
      \includegraphics[height=1cm]{logos/inesc-id.eps}
    };
  \end{tikzpicture}
  }

@@

  \begin{frame}
    \frametitle{Introduction}

    \begin{itemize}
        \color{text}
      \item I am working on an analog implementation of a LSTM Neural Networks.
      \item The final objective of my thesis is to have a successful simulation of such a circuit.
    \end{itemize}

  \begin{frame}
    \frametitle{Introduction}
    \centering\includegraphics[width=\textwidth]{lstm/lstm-np}
  \end{frame}

@@

    There was no meeting last week, and a lot happened but here is what I'm doing :
    \begin{itemize}
      \item Mainly focused on writing the thesis
      \item I also need to run a new simulation with a new problem
    \end{itemize}
  \end{frame}

  \begin{frame}{What's new}
    \begin{itemize}
      \item Results obtianed :
        \begin{itemize}
            \color{text}
          \item None yet
        \end{itemize}
      \item Improvements :
        \begin{itemize}
            \color{text}
          \item
        \end{itemize}
      \item Relevant information :
        \begin{itemize}
            \color{text}
          \item
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}
    \frametitle{Problems/doubts}
    \begin{itemize}
      \item What is the approximate onChip area of an opAmp
      \item What is the precision of a memristor when setting the resistance
      \item I feel like my state of the art is missing content...
      \item When would my thesis defense happen ?
      \item I'm afriad i might not have time to finish on time wiht enough content.
    \end{itemize}
  \end{frame}

@@

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      1 & Figure out the new problem \\
      2 & Digital inference time \\
    \end{tabular}
  \end{frame}

  \begin{frame}{Networking and sharing}
    \begin{tikzpicture}
      \leftRect{Help/Collaboration :}{- I'm looking for a software to create nice looking electronic circuit.}

      \rightRect{Recommendations :}{None}
    \end{tikzpicture}
  \end{frame}
